---
title: "Compilation of feature specific survival analysis-Proteome"
author: "Lavanya"
date: "11/29/2021"
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Compilation of feature specific survival analysis-Proteome}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Calling for packages 

```{r}
packagelist <- c("reshape2", "ggrepel", "ggplot2","dplyr","tidyverse", "formattable","ComplexHeatmap", "pheatmap", "readxl","RColorBrewer","survminer", "survival", "patchwork", "coxme", "conflicted","kableExtra","wesanderson","broom", "gridExtra", "forestplot", "writexl", "GetoptLong","corrplot", "rstatix", "janitor", "org.Hs.eg.db", "clusterProfiler", "msigdbr", "DOSE", "enrichplot", "pathviewr" )

for (i in packagelist){
 suppressPackageStartupMessages(library(i, character.only = TRUE))
}

source("Uni_multi_coxme_Aug2022.r")


conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflicts_prefer(clusterProfiler::rename)
```
a
# IMPORTANT LINKS - 

https://stats.stackexchange.com/questions/411689/cox-regression-different-results-with-different-combinations-of-variables/411817#411817
https://stats.stackexchange.com/questions/68834/what-is-the-benefit-of-breaking-up-a-continuous-predictor-variable https://stats.stackexchange.com/questions/411804/how-to-choose-the-best-combination-of-covariates-in-cox-multiple-regression
https://stackoverflow.com/questions/69780549/convert-cox-regression-table-to-forest-plot

# Calling for Protein survival output files

```{r}
inputname <- list("Protein Cox regression outputs/Early Cytotoxic All_A-Mean.csv",                                                 
                  "Protein Cox regression outputs/Early Cytotoxic All_A-Median.csv" ,                                                   
                  "Protein Cox regression outputs/Early Cytotoxic All_coxME.csv"  ,         
                   "Protein Cox regression outputs/Early Cytotoxic All_fullMergedTable.csv"   ,          
                  
                  "Protein Cox regression outputs/Early Cytotoxic Away_A-Mean.csv"   ,                                                      
                  "Protein Cox regression outputs/Early Cytotoxic Away_A-Median.csv",                                                     
                   "Protein Cox regression outputs/Early Cytotoxic Away_coxME.csv"    ,                                                      
                    "Protein Cox regression outputs/Early Cytotoxic Away_fullMergedTable.csv"      ,   
                  
                  "Protein Cox regression outputs/Early Cytotoxic Within_A-Mean.csv"   ,                    
                    "Protein Cox regression outputs/Early Cytotoxic Within_A-Median.csv"    ,               
                  "Protein Cox regression outputs/Early Cytotoxic Within_coxME.csv"      ,                  
                  "Protein Cox regression outputs/Early Cytotoxic Within_fullMergedTable.csv"   ,
                  
                  "Protein Cox regression outputs/Early Helper All_A-Mean.csv",                                                 
                  "Protein Cox regression outputs/Early Helper All_A-Median.csv" ,                                                   
                  "Protein Cox regression outputs/Early Helper All_coxME.csv"  ,         
                   "Protein Cox regression outputs/Early Helper All_fullMergedTable.csv"   ,          
                  
                  "Protein Cox regression outputs/Early Helper Away_A-Mean.csv"   ,                                                      
                  "Protein Cox regression outputs/Early Helper Away_A-Median.csv",                                                     
                   "Protein Cox regression outputs/Early Helper Away_coxME.csv"    ,                                                      
                    "Protein Cox regression outputs/Early Helper Away_fullMergedTable.csv"      ,   
                  
                  "Protein Cox regression outputs/Early Helper Within_A-Mean.csv"   ,                    
                    "Protein Cox regression outputs/Early Helper Within_A-Median.csv"    ,               
                  "Protein Cox regression outputs/Early Helper Within_coxME.csv"      ,                  
                  "Protein Cox regression outputs/Early Helper Within_fullMergedTable.csv"   ,
                  
                  "Protein Cox regression outputs/Late Cytotoxic All_A-Mean.csv",                                                 
                  "Protein Cox regression outputs/Late Cytotoxic All_A-Median.csv" ,                                                   
                  "Protein Cox regression outputs/Late Cytotoxic All_coxME.csv"  ,         
                   "Protein Cox regression outputs/Late Cytotoxic All_fullMergedTable.csv"   ,          
                  
                  "Protein Cox regression outputs/Late Cytotoxic Away_A-Mean.csv"   ,                                                      
                  "Protein Cox regression outputs/Late Cytotoxic Away_A-Median.csv",                                                     
                   "Protein Cox regression outputs/Late Cytotoxic Away_coxME.csv"    ,                                                      
                    "Protein Cox regression outputs/Late Cytotoxic Away_fullMergedTable.csv"      ,   
                  
                  "Protein Cox regression outputs/Late Cytotoxic Within_A-Mean.csv"   ,                    
                    "Protein Cox regression outputs/Late Cytotoxic Within_A-Median.csv"    ,               
                  "Protein Cox regression outputs/Late Cytotoxic Within_coxME.csv"      ,                  
                  "Protein Cox regression outputs/Late Cytotoxic Within_fullMergedTable.csv"   ,
                  
                    "Protein Cox regression outputs/Late Helper All_A-Mean.csv",                                                 
                  "Protein Cox regression outputs/Late Helper All_A-Median.csv" ,                                                   
                  "Protein Cox regression outputs/Late Helper All_coxME.csv"  ,         
                   "Protein Cox regression outputs/Late Helper All_fullMergedTable.csv"   ,          
                 
                  "Protein Cox regression outputs/Late Helper Within_A-Mean.csv"   ,                    
                    "Protein Cox regression outputs/Late Helper Within_A-Median.csv"    ,               
                  "Protein Cox regression outputs/Late Helper Within_coxME.csv"      ,                  
                  "Protein Cox regression outputs/Late Helper Within_fullMergedTable.csv" , 
                  
                  "Protein Cox regression outputs/Whole data_A-Mean.csv", 
                  "Protein Cox regression outputs/Whole data_A-Median.csv", 
                  "Protein Cox regression outputs/Whole data_coxME.csv",
                  "Protein Cox regression outputs/Whole data_fullMergedTable.csv", 
                  
                  "Protein Cox regression outputs/CD3 Bulk_A-Mean.csv",
                  "Protein Cox regression outputs/CD3 Bulk_A-Median.csv", 
                  "Protein Cox regression outputs/CD3 Bulk_coxME.csv", 
                  "Protein Cox regression outputs/CD3 Bulk_fullMergedTable.csv",
                  
                   "Protein Cox regression outputs/Tumor_A-Mean.csv",
                  "Protein Cox regression outputs/Tumor_A-Median.csv", 
                  "Protein Cox regression outputs/Tumor_coxME.csv", 
                  "Protein Cox regression outputs/Tumor_fullMergedTable.csv"
                  )
                 

outputname <- list( "EC_All_mean", "EC_All_Median", "EC_All_CM", "EC_All_merged",
                    "EC_Away_mean", "EC_Away_Median", "EC_Away_CM", "EC_Away_merged",
                    "EC_Within_mean", "EC_Within_Median", "EC_Within_CM", "EC_Within_merged",
                    
                    "ENC_All_mean", "ENC_All_Median", "ENC_All_CM", "ENC_All_merged",
                    "ENC_Away_mean", "ENC_Away_Median", "ENC_Away_CM", "ENC_Away_merged",
                    "ENC_Within_mean", "ENC_Within_Median", "ENC_Within_CM", "ENC_Within_merged",
                    
                    "LC_All_mean", "LC_All_Median", "LC_All_CM", "LC_All_merged",
                    "LC_Away_mean", "LC_Away_Median", "LC_Away_CM", "LC_Away_merged",
                    "LC_Within_mean", "LC_Within_Median", "LC_Within_CM", "LC_Within_merged",
                    
                    "LNC_All_mean", "LNC_All_Median", "LNC_All_CM", "LNC_All_merged",
                 
                    "LNC_Within_mean", "LNC_Within_Median", "LNC_Within_CM", "LNC_Within_merged", 
                    
                     "WD_mean", "WD_Median", "WD_CM", "WD_merged", 
                    "CD3_mean", "CD3_Median", "CD3_CM", "CD3_merged", 
                    "Tumor_mean", "Tumor_Median", "Tumor_CM", "Tumor_merged"
                   )

datasetname <- list( "EC_All_mean", "EC_All_Median", "EC_All_CM", "EC_All_merged",
                    "EC_Away_mean", "EC_Away_Median", "EC_Away_CM", "EC_Away_merged",
                    "EC_Within_mean", "EC_Within_Median", "EC_Within_CM", "EC_Within_merged",
                    
                    "ENC_All_mean", "ENC_All_Median", "ENC_All_CM", "ENC_All_merged",
                    "ENC_Away_mean", "ENC_Away_Median", "ENC_Away_CM", "ENC_Away_merged",
                    "ENC_Within_mean", "ENC_Within_Median", "ENC_Within_CM", "ENC_Within_merged",
                    
                    "LC_All_mean", "LC_All_Median", "LC_All_CM", "LC_All_merged",
                    "LC_Away_mean", "LC_Away_Median", "LC_Away_CM", "LC_Away_merged",
                    "LC_Within_mean", "LC_Within_Median", "LC_Within_CM", "LC_Within_merged",
                    
                    "LNC_All_mean", "LNC_All_Median", "LNC_All_CM", "LNC_All_merged",
                    
                    "LNC_Within_mean", "LNC_Within_Median", "LNC_Within_CM", "LNC_Within_merged", 
                    "WD_mean", "WD_Median", "WD_CM", "WD_merged", 
                    "CD3_mean", "CD3_Median", "CD3_CM", "CD3_merged",
                    "Tumor_mean", "Tumor_Median", "Tumor_CM", "Tumor_merged"
                   )

datasetname2 <- list( "EC All", "EC All", "EC All", "EC All",
                    "EC Away", "EC Away", "EC Away", "EC Away",
                    "EC Within", "EC Within", "EC Within", "EC Within",
                    
                     "ENC All", "ENC All", "ENC All", "ENC All",
                    "ENC Away", "ENC Away", "ENC Away", "ENC Away",
                    "ENC Within", "ENC Within", "ENC Within", "ENC Within",
                    
                    "LC All", "LC All", "LC All", "LC All",
                    "LC Away", "LC Away", "LC Away", "LC Away",
                    "LC Within", "LC Within", "LC Within", "LC Within",
                    
                    "LNC All", "LNC All", "LNC All", "LNC All",
                    
                    "LNC Within", "LNC Within", "LNC Within", "LNC Within", 
                    
                    "Whole Data", "Whole Data", "Whole Data", "Whole Data", 
                    "Bulk CD3", "Bulk CD3", "Bulk CD3", "Bulk CD3", 
                    "Tumor","Tumor","Tumor","Tumor"
                   )

celltype <- list("EC", "EC","EC","EC",
                 "EC", "EC","EC","EC",
                 "EC", "EC","EC","EC",
                 
                  "ENC", "ENC", "ENC", "ENC",
                  "ENC", "ENC", "ENC", "ENC",
                  "ENC", "ENC", "ENC", "ENC",
                 
                  "LC",  "LC",  "LC",  "LC", 
                 "LC",  "LC",  "LC",  "LC", 
                 "LC",  "LC",  "LC",  "LC", 
                 
                 "LNC", "LNC", "LNC", "LNC",
                 
                  "LNC", "LNC", "LNC", "LNC",
                 "WD", "WD", "WD", "WD", 
                 "Bulk", "Bulk", "Bulk", "Bulk",
                 "Tumor","Tumor","Tumor","Tumor"
                 )

type <- list("Mean", "Median","CM","Merged",
                "Mean", "Median","CM","Merged",
                 "Mean", "Median","CM","Merged",
                 
                 "Mean", "Median","CM","Merged",
                  "Mean", "Median","CM","Merged",
                  "Mean", "Median","CM","Merged",
                 
                "Mean", "Median","CM","Merged",
                "Mean", "Median","CM","Merged",
                "Mean", "Median","CM","Merged",
                 
                 "Mean", "Median","CM","Merged",
                 
                 "Mean", "Median","CM","Merged",
                 "Mean", "Median","CM","Merged",
                 "Mean", "Median","CM","Merged",
               "Mean", "Median","CM","Merged"
                 )



for (i in 1:length(inputname)) {
  dataset <-  read.csv(paste0(inputname[[i]])) %>% as.data.frame() %>% dplyr::mutate(Dataset = paste0(datasetname2[[i]]), Celltype = paste0(celltype[[i]]),ModelType = paste0(type[[i]]), name = paste0(datasetname[[i]])) 
  assign(outputname[[i]], dataset, .GlobalEnv)
}
```

# Clinical data updated November 2022

```{r} 
newclinicaldata <- read_excel("Datafiles/BLISS DATABASE NOVEMBER 2022 - NBIS.xlsx") %>% as.data.frame()
```

# Protein Expression file

```{r}
Proteome <- readxl::read_xlsx("Datafiles/Project2_Protein_all immune subtypes_Sep2023.xlsx") %>% 
  as.data.frame()  %>% 
  rename( "Within.the.tumor"="Within.the.tumor_June2023") %>%  
  dplyr::filter(Within.the.tumor !="Exclude") 

ProteomewithOS <- inner_join(newclinicaldata, Proteome, by = "PATID")
  
ProteomewithOS$OS <- as.numeric(as.character(ProteomewithOS$OS))
ProteomewithOS$OS.01 <- as.numeric(as.character(ProteomewithOS$OS.01))

np <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS)
s <- e-np+1

Proteome %>% select(PATID) %>% distinct()
```

# Merged Heatmap

Note that in cancer studies:

A covariate with hazard ratio > 1 (i.e.: b > 0) is called bad prognostic factor
A covariate with hazard ratio < 1 (i.e.: b < 0) is called good prognostic factor

```{r}
compiled_df <- rbind(Tumor_merged, WD_merged, CD3_merged, EC_All_merged, EC_Away_merged, EC_Within_merged, ENC_All_merged, ENC_Away_merged, ENC_Within_merged, LC_All_merged, LC_Away_merged, LC_Within_merged, LNC_All_merged, LNC_Within_merged)

significance <- 0.05
compiled_df <- compiled_df %>% dplyr::filter(`P_mean`<=significance |`P_med`<=significance | `P_CM` <= significance) %>% dplyr::filter(`P_chk_PH`> significance | `P_chk_CM`> significance | `P_chk_med`> significance | `P_chk_mean`> significance ) %>% dplyr::mutate(Prognosis = ifelse(HR_med > 1 & HR_mean>1 | HR_CM>1, "HR>1", "HR<1") )


comparedf <- compiled_df %>%  select(X, Dataset, Prognosis) %>% dcast(X~Dataset) %>% as.data.frame() %>% replace(is.na(.), "n.s") 
row.names(comparedf) <- comparedf$X
mycol <- colorRampPalette(brewer.pal(10, "Pastel2"))(3)

df <- names(comparedf) %>% as.data.frame() %>% row_to_names(row_number = 1) 
df <-df %>% dplyr::mutate(Region = ifelse(grepl("Away", df$X), "Tumor-depleted", ifelse(grepl("Within", df$X), "Tumor-rich",  ifelse(grepl("All", df$X), "Localization Undivided",  ifelse(grepl("Bulk CD3", df$X), "Bulk T cells",  ifelse(grepl("Whole Data", df$X), "Cell type undivided", "Tumor"))))), SegmentType = ifelse(grepl("EC", df$X), "Early Cytotoxic", ifelse(grepl("ENC", df$X), "Early Helper",  ifelse(grepl("LC", df$X), "Late Cytotoxic",  ifelse(grepl("Bulk CD3", df$X), "Bulk T cells",  ifelse(grepl("Whole Data", df$X), "Cell type undivided",  ifelse(grepl("LNC", df$X), "Late Helper", "Tumor")))))))
                
column_ha = HeatmapAnnotation(CellType = df$SegmentType, Region = df$Region, col = list(CellType = c("Tumor"= "#fee391", "Bulk T cells"= "#d4b9da","Cell type undivided"= "navyblue", "Early Cytotoxic"="#41ae76","Early Helper"= "#e7298a","Late Cytotoxic"= "goldenrod2", "Late Helper"="#67a9cf"), Region = c("Tumor"= "#fee391", "Bulk T cells"="#d4b9da","Cell type undivided"= "navyblue", "Localization Undivided"="papayawhip", "Tumor-rich" = "#980043", "Tumor-depleted"="#fd8d3c")))

Heatmap(as.matrix(comparedf %>% select(-c(X))), row_names_gp = gpar(fontsize = 10),  column_names_gp = gpar(fontsize =10),  row_names_centered = FALSE, column_names_centered = FALSE,  show_heatmap_legend = TRUE,  row_names_side = "left", row_labels = comparedf$X, show_row_names = TRUE, rect_gp = gpar(col = "white", lwd = 2), col  = c("HR<1" ='#2ca25f',"HR>1" = '#ef3b2c', "n.s" = "#e0ecf4"), heatmap_legend_param = list(title = "Significance"), top_annotation = column_ha, column_split = df$SegmentType,show_column_names = FALSE, column_title=NULL,row_title=NULL, column_gap  = unit(2, "mm"), border = TRUE)

```

```{r}
compiled_df <- rbind(Tumor_CM, WD_CM, CD3_CM, EC_All_CM, EC_Away_CM, EC_Within_CM, ENC_All_CM, ENC_Away_CM, ENC_Within_CM, LC_All_CM, LC_Away_CM, LC_Within_CM, LNC_All_CM, LNC_Within_CM)
significance <- 0.05
compiled_df <- compiled_df %>% dplyr::filter(Pvalue <= significance) %>% dplyr::filter(Pvalue_check > significance ) %>% dplyr::mutate(Prognosis = ifelse( HR>1, "HR>1", "HR<1") )

comparedf <- compiled_df %>%  select(Biomarkers, Dataset, Prognosis) %>% dcast(Biomarkers~Dataset) %>% as.data.frame() %>% replace(is.na(.), "n.s") 
row.names(comparedf) <- comparedf$Biomarkers
mycol <- colorRampPalette(brewer.pal(10, "Pastel2"))(3)

df <- names(comparedf) %>% as.data.frame() %>% row_to_names(row_number = 1) 
df <-df %>% dplyr::mutate(Region = ifelse(grepl("Away", df$Biomarkers), "Tumor-depleted", ifelse(grepl("Within", df$Biomarkers), "Tumor-rich",  ifelse(grepl("All", df$Biomarkers), "Localization Undivided",  ifelse(grepl("Bulk CD3", df$Biomarkers), "Bulk T cells",  ifelse(grepl("Whole Data", df$Biomarkers), "Cell type undivided", "Tumor"))))), SegmentType = ifelse(grepl("EC", df$Biomarkers), "Early Cytotoxic", ifelse(grepl("ENC", df$Biomarkers), "Early Helper",  ifelse(grepl("LC", df$Biomarkers), "Late Cytotoxic",  ifelse(grepl("Bulk CD3", df$Biomarkers), "Bulk T cells",  ifelse(grepl("Whole Data", df$Biomarkers), "Cell type undivided",  ifelse(grepl("LNC", df$Biomarkers), "Late Helper", "Tumor")))))))
                
column_ha = HeatmapAnnotation(CellType = df$SegmentType, Region = df$Region, col = list(CellType = c("Tumor"= "#fee391", "Bulk T cells"= "#d4b9da","Cell type undivided"= "navyblue", "Early Cytotoxic"="#41ae76","Early Helper"= "#e7298a","Late Cytotoxic"= "goldenrod2", "Late Helper"="#67a9cf"), Region = c("Tumor"= "#fee391", "Bulk T cells"="#d4b9da","Cell type undivided"= "navyblue", "Localization Undivided"="mistyrose", "Tumor-rich" = "#980043", "Tumor-depleted"="#fd8d3c")))

Heatmap(as.matrix(comparedf %>% select(-c(Biomarkers))), row_names_gp = gpar(fontsize = 10),  column_names_gp = gpar(fontsize =10),  row_names_centered = FALSE, column_names_centered = FALSE,  show_heatmap_legend = TRUE,  row_names_side = "left", row_labels = comparedf$Biomarkers, show_row_names = TRUE, rect_gp = gpar(col = "white", lwd = 2), col  = c("HR<1" ='#2ca25f',"HR>1" = '#ef3b2c', "n.s" = "#e0ecf4"), heatmap_legend_param = list(title = "Significance"), top_annotation = column_ha, column_split = df$SegmentType,show_column_names = FALSE, column_title=NULL,row_title=NULL, column_gap  = unit(2, "mm"), border = TRUE)

```


# Kaplan meier curves for protein list

```{r}
KMCatCurves(data = ProteomewithOS, inputlist = comparedf$Biomarkers, filterCV = TRUE, PATID = "PATID",CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

<!-- ```{r} -->
<!-- logrankFilter <- function(data, inputlist, filterCV = FALSE, PATID, CVcutoff = 30, aggregationType = c(NULL, "mean", "median"), SurvCutoff = TRUE, minprop = 0.1){ -->
<!--   splots <- data.frame() -->
<!--   for (i in inputlist) { -->
<!--     data[[i]] <- as.numeric(as.character(data[[i]])) -->


<!--     if (filterCV == TRUE) { -->
<!--       cvlist <- filterCV(data=data, PATID = PATID, names=paste0(i)) -->
<!--       cvlist <- cvlist %>%  dplyr::filter(CV <= CVcutoff) -->

<!--       data <- subset(data, data$PATID %in% cvlist$PATID) %>% as.data.frame() -->
<!--     } -->

<!--     aggregationType <- match.arg(aggregationType) -->

<!--     if (aggregationType == "median") { -->

<!--       datanew <- data%>% select(PATID, OS, OS.01, paste0(i)) %>% dplyr::group_by(PATID) %>% summarise_if(is.numeric, median) %>% as.data.frame() -->
<!--       Median_cutoff <- logrankmedianfilter(inputdata=datanew, i=paste0(i)) -->

<!--       if (SurvCutoff == TRUE) { -->


<!--         cutpoint <- surv_cutpoint(datanew,time = "OS",event = "OS.01",variables = paste0(i), minprop = minprop) -->
<!--         res.cat <- surv_categorize(cutpoint) -->
<!--         res.cat[[i]] <- as.factor(res.cat[[i]]) -->
<!--         res.cat<-res.cat[complete.cases(res.cat),] -->

<!--         f1 <- as.formula(paste0("Surv(OS, OS.01) ~", i)) -->
<!--         fit <- do.call(survdiff, args = list(formula = f1, data = res.cat)) -->
<!--         Survcutoff <- 1 - pchisq(fit$chisq, length(fit$n) - 1) -->

<!--         collated <-  cbind(paste0(i), Median_cutoff, Survcutoff) -->
<!--         splots <- splots %>% rbind(collated)   -->


<!--       }else { -->
<!--         collated <-  cbind(paste0(i), Median_cutoff) -->
<!--         splots <- splots %>% rbind(collated) -->
<!--       } -->

<!--     } else if (aggregationType == "mean") { -->

<!--       datanew <- data %>% select(PATID, OS, OS.01, paste0(i)) %>%  dplyr::group_by(PATID) %>% summarise_if(is.numeric, mean) %>% as.data.frame() -->
<!--       Median_cutoff <- logrankmedianfilter(inputdata=datanew, i=paste0(i)) -->

<!--       if (SurvCutoff == TRUE) { -->
<!--         splots <- list() -->
<!--         cutpoint <- surv_cutpoint(datanew,time = "OS",event = "OS.01",variables = paste0(i), minprop = minprop) -->

<!--         res.cat <- surv_categorize(cutpoint) -->
<!--         res.cat[[i]] <- as.factor(res.cat[[i]]) -->
<!--         res.cat<-res.cat[complete.cases(res.cat),] -->

<!--         f1 <- as.formula(paste0("Surv(OS, OS.01) ~", i)) -->
<!--         fit <- do.call(survdiff, args = list(formula = f1, data = res.cat)) -->
<!--         Survcutoff <- 1 - pchisq(fit$chisq, length(fit$n) - 1) -->

<!--         collated <-  cbind(paste0(i), Median_cutoff, Survcutoff) -->
<!--         splots <- splots %>% rbind(collated)   -->

<!--       }else { -->
<!--         collated <-  cbind(paste0(i), Median_cutoff) -->
<!--         splots <- splots %>% rbind(collated) -->
<!--       } -->


<!--     } else if (is.null(aggregationType)) { -->
<!--       Median_cutoff <- logrankmedianfilter(inputdata=datanew, i=paste0(i)) -->

<!--       if (SurvCutoff == TRUE) { -->
<!--         splots <- list() -->
<!--         cutpoint <- surv_cutpoint(data,time = "OS",event = "OS.01",variables = paste0(i), minprop = minprop) -->

<!--         res.cat <- surv_categorize(cutpoint) -->
<!--         res.cat[[i]] <- as.factor(res.cat[[i]]) -->
<!--         res.cat<-res.cat[complete.cases(res.cat),] -->

<!--         f1 <- as.formula(paste0("Surv(OS, OS.01) ~", i)) -->
<!--         fit <- do.call(survdiff, args = list(formula = f1, data = res.cat)) -->
<!--         Survcutoff <- 1 - pchisq(fit$chisq, length(fit$n) - 1) -->
<!--         collated <-  cbind(paste0(i), Median_cutoff, Survcutoff) -->
<!--         splots <- splots %>% rbind(collated)   -->

<!--       }else { -->
<!--         collated <-  cbind(paste0(i), Median_cutoff) -->
<!--         splots <- splots %>% rbind(collated) -->
<!--       } -->
<!--     } -->
<!--   } -->
<!--   return(splots) -->
<!-- } -->


<!-- check <- surv_cutpoint(ProteomewithOS,time = "OS",event = "OS.01",variables = "p53", minprop = 0.1) -->
<!-- ``` -->


<!-- # Functional enrichment  -->

<!-- ```{r} -->
<!-- Listnames <- comparedf %>%  filter(X!="BAD") %>% select(X) -->

<!-- mappedids <- readxl::read_xlsx("Datafiles/MappedIds_Active.xlsx", sheet = "keggadded") %>% as.data.frame() -->
<!-- mappedids <- subset(mappedids ,mappedids$ProteinID %in% Listnames$X) %>%  arrange(desc(kegg)) -->
<!-- eg = bitr(mappedids$ENSEMBL, fromType="ENSEMBL", toType="ENTREZID", OrgDb="org.Hs.eg.db") -->

<!-- genelist <-unique(mappedids$kegg) -->
<!-- ``` -->

<!-- ## MsigDB enrichment -->
<!-- ```{r} -->
<!-- m_t2g <- msigdbr(species = "Homo sapiens", category = "C5") %>% dplyr::select(gs_name, entrez_gene) -->
<!-- ego1 <- enricher(genelist, TERM2GENE=m_t2g) -->
<!-- ``` -->

<!-- ### Barplot -->
<!-- ```{r} -->
<!-- dplyr::mutate(ego1, qscore = -log(p.adjust, base=10)) %>% barplot(x="qscore") -->
<!-- ``` -->

<!-- ### Dotplot -->
<!-- ```{r} -->
<!-- conflict_prefer("desc", "dplyr") -->
<!-- dotplot(ego1, showCategory=10) -->
<!-- ``` -->

<!-- ### Upsetplot -->
<!-- ```{r} -->
<!-- upsetplot(ego1) -->
<!-- ``` -->

<!-- ### CnetPlot -->
<!-- ```{r} -->
<!-- cnetplot(ego1, foldChange=genelist,circular = TRUE, colorEdge = TRUE, showCategory = 10, node_label="category",  -->
<!--         cex_label_category = 1.2,) -->
<!-- ``` -->

<!-- ## Kegg enrichment -->

<!-- ```{r} -->
<!-- kk <- enrichKEGG(gene = eg$ENTREZID, -->
<!-- organism = 'hsa', -->
<!-- pvalueCutoff = 0.05) -->

<!-- head(kk) -->

<!-- listID <-  kk@result[["ID"]] %>% as.data.frame() %>% slice_head(n=10) -->

<!-- for (i in listID$.) { -->
<!--   pathview(gene.data  = genelist, -->
<!--                    pathway.id = i,  -->
<!--                      species    = "hsa",kegg.native = T) -->
<!-- } -->
<!-- ``` -->

<!-- ### Barplot -->
<!-- ```{r} -->
<!-- dplyr::mutate(kk, qscore = -log(p.adjust, base=10)) %>% barplot(x="qscore") -->
<!-- barplot(kk, showCategory = 20) -->
<!-- ``` -->

<!-- ### Dotplot -->
<!-- ```{r} -->
<!-- dotplot(kk,  showCategory = 10) -->
<!-- ``` -->

<!-- ### Upsetplot -->
<!-- ```{r} -->
<!-- upsetplot(kk) -->
<!-- ``` -->

<!-- ### CnetPlot -->
<!-- ```{r} -->
<!-- cnetplot(kk, foldChange=genelist,colorEdge = TRUE, showCategory = 10, node_label="category",  -->
<!--         cex_label_category = 1.2,) -->
<!-- ``` -->

<!-- ## Wikipathways enrichment -->
<!-- ```{r} -->
<!-- WP <- enrichWP(genelist, organism = "Homo sapiens")  -->
<!-- ``` -->

<!-- ### Barplot -->
<!-- ```{r, ,echo=FALSE, fig.height=3, fig.width=4} -->
<!-- dplyr::mutate(WP, qscore = -log(p.adjust, base=10)) %>% barplot(x="qscore", showCategory = 15) -->
<!-- barplot(WP, showCategory = 15) -->
<!-- ``` -->

<!-- ### Dotplot -->
<!-- ```{r} -->
<!-- conflict_prefer("desc", "dplyr") -->
<!-- dotplot(WP, showCategory=20) -->
<!-- ``` -->

<!-- ### Upsetplot -->
<!-- ```{r,echo=FALSE, fig.height=3, fig.width=12} -->
<!-- #pdf("WP_upsetplot.pdf", width = 40, height = 20) -->
<!-- upsetplot(WP) -->
<!-- #dev.off() -->
<!-- ``` -->

<!-- ### CnetPlot -->
<!-- ```{r, ,echo=FALSE, fig.height=5, fig.width=12} -->
<!-- cnetplot(WP, foldChange=genelist,circular = TRUE, colorEdge = TRUE, showCategory = 10, node_label="category",  -->
<!--         cex_label_category = 0.8) -->
<!-- ``` -->


<!-- # Boxplot analysis with CV removal -->

<!-- ```{r} -->
<!-- CVcutoff <-10 -->
<!-- marker <- "FOXP3" -->
<!-- data_EC <-   Proteome %>% filter(Segment_name_label=="Early Cytotoxic") -->
<!-- cvlist <- filterCV(data= data_EC,  PATID = "PATID", names=marker) -->
<!-- cvlist <- cvlist %>%  dplyr::filter(CV <= CVcutoff) -->
<!-- data_EC <- subset(data_EC, data_EC$PATID %in% cvlist$PATID) %>% as.data.frame() -->

<!-- data_ENC <-   Proteome %>% filter(Segment_name_label=="Early Helper") -->
<!-- cvlist <- filterCV(data= data_ENC,  PATID = "PATID", names=marker) -->
<!-- cvlist <- cvlist %>%  dplyr::filter(CV <= CVcutoff) -->
<!-- data_ENC <- subset(data_ENC, data_ENC$PATID %in% cvlist$PATID) %>% as.data.frame() -->

<!-- data_LC <-   Proteome %>% filter(Segment_name_label=="Late Cytotoxic") -->
<!-- cvlist <- filterCV(data= data_LC,  PATID = "PATID", names=marker) -->
<!-- cvlist <- cvlist %>%  dplyr::filter(CV <= CVcutoff) -->
<!-- data_LC <- subset(data_LC, data_LC$PATID %in% cvlist$PATID) %>% as.data.frame() -->

<!-- data_LNC <-   Proteome %>% filter(Segment_name_label=="Late Helper") -->
<!-- cvlist <- filterCV(data= data_LNC,  PATID = "PATID", names=marker) -->
<!-- cvlist <- cvlist %>%  dplyr::filter(CV <= CVcutoff) -->
<!-- data_LNC <- subset(data_LNC, data_LNC$PATID %in% cvlist$PATID) %>% as.data.frame() -->

<!-- CVfiltereddf <-  rbind(data_EC, data_ENC, data_LC, data_LNC) -->

<!-- my_comparisons <- list( c("Early Cytotoxic", "Early Helper"), c("Early Cytotoxic", "Late Cytotoxic"), c("Early Cytotoxic", "Late Helper") ) -->

<!-- Proteome %>% ggplot(aes(x=Segment_name_label, y=FOXP3, fill = Segment_name_label)) + -->
<!--   geom_violin(alpha = 0.6) + -->
<!--   geom_jitter(width=0.2, height=0.1, alpha = 0.2, size = 2) + -->
<!--   stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value -->
<!--   stat_compare_means(label.y = 9)  +   # Add global p-value -->
<!--   theme(axis.ticks.x = element_line(size = 0.1),axis.title.y = element_text(size = 12),panel.background = element_rect(fill = "white"),panel.border = element_rect(fill = NA), legend.position = "none", legend.title = element_blank(), legend.text = element_text(size = 10))  -->
<!-- ``` -->
