---
title: "Feature specific survival analysis - Protein, without CV"
author: "Lavanya"
date: "11/29/2021"
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Feature specific survival analysis - Protein, without CV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Calling for packages 

```{r}
packagelist <- c("reshape", "ggrepel", "ggplot2","dplyr","tidyverse", "formattable","ComplexHeatmap", "pheatmap", "readxl","RColorBrewer","survminer", "survival", "patchwork", "coxme", "conflicted","kableExtra","wesanderson","broom", "gridExtra", "writexl", "GetoptLong","corrplot")

for (i in packagelist){
 suppressPackageStartupMessages(library(i, character.only = TRUE))
}

source("Function list.R") 
source("KMCatCurves.R")
source("Uni_multi_coxme_Aug2022.r")

conflict_prefer("filter", "dplyr")
conflicts_prefer(dplyr::rename)
```

# IMPORTANT LINKS - 

https://stats.stackexchange.com/questions/411689/cox-regression-different-results-with-different-combinations-of-variables/411817#411817
https://stats.stackexchange.com/questions/68834/what-is-the-benefit-of-breaking-up-a-continuous-predictor-variable https://stats.stackexchange.com/questions/411804/how-to-choose-the-best-combination-of-covariates-in-cox-multiple-regression
https://stackoverflow.com/questions/69780549/convert-cox-regression-table-to-forest-plot

# Clinical data updated November 2022

```{r} 
newclinicaldata <- read_excel("Datafiles/BLISS DATABASE NOVEMBER 2022 - NBIS.xlsx") %>% as.data.frame()
```

# T-cell Protein Expression file

```{r}
Proteome <- readxl::read_xlsx("Datafiles/Project2_Protein_all immune subtypes_Sep2023.xlsx") %>% 
  as.data.frame()  %>% 
  rename("Within.the.tumor"="Within.the.tumor_June2023") %>%  
  dplyr::filter(Within.the.tumor !="Exclude") 

ProteomewithOS <- inner_join(newclinicaldata, Proteome, by = "PATID")
  
ProteomewithOS$OS <- as.numeric(as.character(ProteomewithOS$OS))
ProteomewithOS$OS.01 <- as.numeric(as.character(ProteomewithOS$OS.01))

np <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS)
s <- e-np+1

Proteome %>% select(PATID) %>% distinct()

ProteomewithOS[,s:e]
```

# Comparing to cox model formulas to optimise for best model

Function adapted from  http://rstudio-pubs-static.s3.amazonaws.com/16621_8843f393472f4e8793435462d8c4859e.html 

NOTE - 
""Oka suggested using frailty in connection with coxph in order to test the proportional hazard assumption. I believe it is worth noting that the documentation for frailty mentions, "the coxme package has superseded this [frailty] method." For this reason, the original question about "how to test the PH assumption on mixed effect cox model coxme," has strong justification to stay within the scope of coxme."" - Stack Overflow

USING COX.ZPH to check for the validity of Cox - https://stats.stackexchange.com/questions/254471/coxme-proportional-hazard-assumption 

```{r}
fit0 <- coxph(Surv(as.numeric(as.character(ProteomewithOS$OS)), as.numeric(as.character(ProteomewithOS$OS.01))) ~ 1, data=ProteomewithOS)
fit1 <- coxph(Surv(as.numeric(as.character(ProteomewithOS$OS)), as.numeric(as.character(ProteomewithOS$OS.01))) ~ IDO1, data=ProteomewithOS)
#Random effects are specified in the formula by a parenthesised expression which contains a vertical bar separating effects on the left from grouping variables on the right. In the case above we read it as an intercept (effect) per center (group).
fit2 <- coxme(Surv(as.numeric(as.character(ProteomewithOS$OS)), as.numeric(as.character(ProteomewithOS$OS.01))) ~ IDO1+ (1|PATID), data=ProteomewithOS)

Compare_models(baseModel = fit0,coxphModel=fit1, coxmeModel=fit2)
```

# Cox regression models

## Whole data 
```{r}
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS)
s <- e-n+1

Inputlistdf <- Uni_multi_coxme(data = ProteomewithOS, name = "Whole data", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS, inputlist = c(rownames(Inputlistdf), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## Early Cytotoxic

### All patients (not segmented in localization)

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Cytotoxic")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_EC_all <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Cytotoxic All", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_EC_all), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Within The Tumor

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Cytotoxic") %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_EC_W <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Cytotoxic Within", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_EC_W), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Away from the Tumor

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Cytotoxic") %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_EC_A <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Cytotoxic Away", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_EC_A), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## Early Helper

### All patients (not segmented in localization)

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Helper")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_ENC_all <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Helper All", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_ENC_all), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Within The Tumor

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Helper") %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_ENC_W <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Helper Within", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_ENC_W), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Away from the Tumor

```{r}
source("Uni_multi_coxme_Aug2022.r")
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Early Helper") %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_ENC_A <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Early Helper Away", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_ENC_A), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```


## Late Helper

### All patients (not segmented in localization)

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Helper")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_LNC_all <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Helper All", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_LNC_all), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Within The Tumor

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Helper") %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_LNC_W <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Helper Within", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = c(rownames(Inputlistdf_LNC_W), "IDO1", "GITR"), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Away from the Tumor

Only 7 samples remained

```{r}
# ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Helper") %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
# n <- 62 ## no of markers (- histone_H3)
# e <- ncol(ProteomewithOS_subset)
# s <- e-n+1
# 
# Inputlistdf_LNC_A <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Helper Away", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)
# 
# KMCatCurves(data = ProteomewithOS_subset, inputlist = rownames(Inputlistdf_LNC_A), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## Late Cytotoxic

### All patients (not segmented in localization)

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Cytotoxic")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_LC_all <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Cytotoxic All", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = rownames(Inputlistdf_LC_all), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Within The Tumor

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Cytotoxic") %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_LC_W <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Cytotoxic Within", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = rownames(Inputlistdf_LC_W), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Away from the Tumor

Only 10 samples remained

```{r}
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(SegmentLabel == "Late Cytotoxic") %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset)
s <- e-n+1

Inputlistdf_LC_A <- Uni_multi_coxme(data = ProteomewithOS_subset, name = "Late Cytotoxic Away", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset, inputlist = rownames(Inputlistdf_LC_A), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## All subtypes segmented "Within the tumor", paired 39 patients 

```{r}
test <- inner_join(ProteomewithOS %>% dplyr::filter(Within.the.tumor=="Tumor-sparse") %>% dplyr::select(PATID, SegmentLabel) %>% mutate(combined = paste0(PATID, SegmentLabel)), ProteomewithOS %>% dplyr::filter(Within.the.tumor=="Tumor-rich") %>% dplyr::select(PATID, SegmentLabel)%>% mutate(combined = paste0(PATID, SegmentLabel)), by = "combined") 

paired_pat <- unique(test$PATID.x)

ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(PATID %in% paired_pat)

test <- ProteomewithOS_subset%>% dplyr::filter(Within.the.tumor=="Tumor-rich") %>% select(PATID)
length(unique(test$PATID))
```

### Early Cytotoxic

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Early Cytotoxic", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_EC_PP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Early Cytotoxic Within Paired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_EC_PP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Early Helper

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Early Helper", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_ENC_PP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Early Helper Within Paired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_ENC_PP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Late Cytotoxic

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Late Cytotoxic", Within.the.tumor=="Tumor-rich")

n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_LC_PP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Late Cytotoxic Within Paired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_LC_PP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Late Helper

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Late Helper", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_LNC_PP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Late Helper Within Paired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_LNC_PP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## All subtypes segmented "Within the tumor", not paired 39 patients 

```{r}
`%NOTin%` <- Negate(`%in%`)
ProteomewithOS_subset <- ProteomewithOS %>% dplyr::filter(PATID %NOTin% paired_pat)

test <- ProteomewithOS_subset%>% dplyr::filter(Within.the.tumor=="Tumor-rich") %>% select(PATID)
length(unique(test$PATID))
```

### Early Cytotoxic

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Early Cytotoxic", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_EC_NPP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Early Cytotoxic Within NotPaired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_EC_NPP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Early Helper

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Early Helper", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_ENC_NPP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Early Helper Within NotPaired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_ENC_NPP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Late Cytotoxic

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Late Cytotoxic", Within.the.tumor=="Tumor-rich")

n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_LC_NPP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Late Cytotoxic Within NotPaired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_LC_NPP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

### Late Helper

```{r}
ProteomewithOS_subset2 <- ProteomewithOS_subset %>% dplyr::filter(SegmentLabel == "Late Helper", Within.the.tumor=="Tumor-rich")
n <- 62 ## no of markers (- histone_H3)
e <- ncol(ProteomewithOS_subset2)
s <- e-n+1

Inputlistdf_LNC_NPP <- Uni_multi_coxme(data = ProteomewithOS_subset2, name = "Late Helper Within NotPaired", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = ProteomewithOS_subset2, inputlist = rownames(Inputlistdf_LNC_NPP), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## Tumor Cells

```{r}
n <- 62 ## no of markers (- neg)

CD20prot <- read_excel("Datafiles/PCD20_Sep2023.xlsx") %>% as.data.frame() %>% rename("X4.1BB"="4.1BB")

CD20protwithOS <- inner_join(newclinicaldata, CD20prot, by = "PATID") %>% as.data.frame()
e <- ncol(CD20protwithOS)
s <- e-n+1

CD20protwithOS$OS <- as.numeric(as.character(CD20protwithOS$OS))
CD20protwithOS$OS.01 <- as.numeric(as.character(CD20protwithOS$OS.01))

Inputlistdf_Tumor <- Uni_multi_coxme(data = CD20protwithOS, name = "Tumor", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = CD20protwithOS, inputlist = rownames(Inputlistdf_Tumor), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)
```

## Bulk CD3+ T Cells

```{r}
CD3prot<- read_excel("Datafiles/PCD3_Sep2023.xlsx") %>% as.data.frame()  %>% rename("X4.1BB"="4.1BB")
CD3protwithOS <- inner_join(newclinicaldata, CD3prot, by = "PATID") %>% as.data.frame()
n=62
e <- ncol(CD3protwithOS)
s <- e-n+1

Inputlistdf_CD3 <- Uni_multi_coxme(data = CD3protwithOS, name = "CD3 Bulk", s=s, e=e, outputfilepath ="Results_images_featurespecific/", uniquefactortype  = "SegmentLabel",printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, Time = "OS",Event = "OS.01", CVcutoff = 30, PATID = "PATID", significance = 0.05)

KMCatCurves(data = CD3protwithOS, inputlist = rownames(Inputlistdf_CD3), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1, SurvCutoff = TRUE)

CD3protwithOS[,s:e]
```

## Treatment subset 

### NLG-MCL2

```{r}
# "NLG-MCL2"     "Bendamustin"  NA             "Chlorambucil" "CHOP"     
unique(CD20protwithOS$Treatment)
data <- CD20protwithOS %>%  dplyr::filter(Treatment == "NLG-MCL2") %>% as.data.frame()
datanew <- data %>% dplyr::group_by(PATID) %>% summarise_if(is.numeric, median) %>% as.data.frame()

cutpoint <- surv_cutpoint(datanew,time = "OS",event = "OS.01",variables = "BIM", minprop = 0.1)
plot(cutpoint) 
res.cat <- surv_categorize(cutpoint)
fit <- survfit(Surv(as.numeric(as.character(OS)), as.numeric(as.character(OS.01))) ~ BIM, data = res.cat)
survminer::ggsurvplot(fit, data = res.cat, pval = TRUE, conf.int = TRUE,
                                       risk.table = TRUE, # Add risk table
                                       risk.table.col = "strata", # Change risk table color by groups
                                       linetype = "strata", # Change line type by groups
                                       surv.median.line = "hv", # Specify median survival
                                       ggtheme = theme_bw(), # Change ggplot2 theme
                                       title = "Surv cutpoint",
                                       palette = c("#02818a", "#ae017e"),
                                       legend.labs = c("High", "Low"), font.x = 10, font.y = 10,font.legend = 10, font.title=8)
        

med <-  median(as.numeric(as.character(datanew$BIM)), na.rm = TRUE)
datanew <- datanew %>% mutate(Cat = ifelse(datanew$BIM<med, "Low", "High"))
  
fit <- survfit(Surv(as.numeric(as.character(OS)), as.numeric(as.character(OS.01))) ~ Cat, data = datanew)

plot <- survminer::ggsurvplot(fit, data = datanew, pval = TRUE, conf.int = TRUE,
risk.table = TRUE, # Add risk table
risk.table.col = "strata", # Change risk table color by groups
linetype = "strata", # Change line type by groups
surv.median.line = "hv", # Specify median survival
ggtheme = theme_bw(), # Change ggplot2 theme
title = "Median cutpoint",palette = c("#02818a", "#ae017e"))
print(plot)
```

### Bendamustin

```{r}
# "NLG-MCL2"     "Bendamustin"  NA             "Chlorambucil" "CHOP"     
unique(CD20protwithOS$Treatment)
data <- CD20protwithOS %>%  dplyr::filter(Treatment == "R-Bendamustine") %>% as.data.frame()
datanew <- data %>% dplyr::group_by(PATID) %>% summarise_if(is.numeric, median) %>% as.data.frame()

cutpoint <- surv_cutpoint(datanew,time = "OS",event = "OS.01",variables = "BIM", minprop = 0.1)
plot(cutpoint) 
res.cat <- surv_categorize(cutpoint)
fit <- survfit(Surv(as.numeric(as.character(OS)), as.numeric(as.character(OS.01))) ~ BIM, data = res.cat)
survminer::ggsurvplot(fit, data = res.cat, pval = TRUE, conf.int = TRUE,
                                       risk.table = TRUE, # Add risk table
                                       risk.table.col = "strata", # Change risk table color by groups
                                       linetype = "strata", # Change line type by groups
                                       surv.median.line = "hv", # Specify median survival
                                       ggtheme = theme_bw(), # Change ggplot2 theme
                                       title = "Surv cutpoint",
                                       palette = c("#02818a", "#ae017e"),
                                       legend.labs = c("High", "Low"), font.x = 10, font.y = 10,font.legend = 10, font.title=8)
        

med <-  median(as.numeric(as.character(datanew$BIM)), na.rm = TRUE)
datanew <- datanew %>% mutate(Cat = ifelse(datanew$BIM<med, "Low", "High"))
  
fit <- survfit(Surv(as.numeric(as.character(OS)), as.numeric(as.character(OS.01))) ~ Cat, data = datanew)

plot <- survminer::ggsurvplot(fit, data = datanew, pval = TRUE, conf.int = TRUE,
risk.table = TRUE, # Add risk table
risk.table.col = "strata", # Change risk table color by groups
linetype = "strata", # Change line type by groups
surv.median.line = "hv", # Specify median survival
ggtheme = theme_bw(), # Change ggplot2 theme
title = "Median cutpoint",palette = c("#02818a", "#ae017e"))
print(plot)
```

