---
title: "Feature specific survival analysis for CTA, CV set as FALSE"
author: "Lavanya"
output:
  BiocStyle::html_document:
    toc_float: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Feature specific survival analysis for CTA, CV set as FALSE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Calling for packages 

```{r}
packagelist <- c("reshape", "ggrepel", "ggplot2","dplyr","tidyverse", "formattable","ComplexHeatmap", "pheatmap", "readxl","RColorBrewer","survminer", "survival", "patchwork", "coxme", "conflicted","kableExtra","wesanderson","broom", "gridExtra", "writexl", "GetoptLong","corrplot", "ggpmisc")

for (i in packagelist){
 suppressPackageStartupMessages(library(i, character.only = TRUE))
}
source("Function list.R")

conflicts_prefer(dplyr::rename)
conflict_prefer("filter", "dplyr")
source("Uni_multi_coxme_Aug2022.r")
```

# Palettes used

```{r}
customGreen0 = "#DeF7E9"
customGreen = "#71CA97"
customRed = "#ff7f7f"

cols = c("up" = "#e41a1c", "down" = "blue", "ns" = "grey", "DE" = "#ffad73")
cols = c("Enriched in low" = "red", "Enriched in high" = "blue", "ns" = "grey")
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))

sizes <- c("Enriched in low" = 2, "Enriched in high" = 2, "ns" = 1, "DE" = 2)

cols2 <- brewer.pal(n = 9, name = "Spectral")
pal1 <- colorRampPalette(cols2)

cols3 <- brewer.pal(n = 11, name = "RdBu")
pal2 <- colorRampPalette(cols3)

my_colour = list(Direction = c("Enriched in low" = "#5977ff", "Enriched in high" = "#f74747"), `Within the tumor` = c("Away" = "#1B9E77", "Within"="#D95F02"))
heatmap_color <- colorRampPalette(c("green", "black", "firebrick3"))(50)


#paired_pat <- readxl::read_xlsx("Datafiles/Paired-PATID.xlsx") 
#writexl::write_xlsx(paired_pat, "Paired-PATID.xlsx")
```

# IMPORTANT LINKS - 

https://stats.stackexchange.com/questions/411689/cox-regression-different-results-with-different-combinations-of-variables/411817#411817
https://stats.stackexchange.com/questions/68834/what-is-the-benefit-of-breaking-up-a-continuous-predictor-variable https://stats.stackexchange.com/questions/411804/how-to-choose-the-best-combination-of-covariates-in-cox-multiple-regression
https://stackoverflow.com/questions/69780549/convert-cox-regression-table-to-forest-plot

# Calling for input normalyzed data

```{r}
CTA <- readxl::read_xlsx("Datafiles/Project_3_immune_MTC_MTH_Sep2023.xlsx") %>% as.data.frame() 

n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA)-n 
startwithNPC <- s-1 
e <- ncol(CTA)

head(CTA[,s:e])

tumormrna <- read_excel("Datafiles/MCD20_Sep 2023.xlsx") %>% as.data.frame() 

tumormrna %>% select(PATID) %>% distinct()
```

## Clinical data updated November 2022

```{r} 
newclinicaldata <- read_excel("Datafiles/BLISS DATABASE NOVEMBER 2022 - NBIS.xlsx") %>% as.data.frame()
```

## Subsetting the main df

```{r}
CTA_tumor <-  inner_join(newclinicaldata, tumormrna, by = "PATID")
CTA_cyto <- inner_join(newclinicaldata, CTA, by = "PATID") %>% dplyr::filter(SegmentLabelNew == "MTC")
CTA_helper <- inner_join(newclinicaldata, CTA, by = "PATID") %>% dplyr::filter(SegmentLabelNew == "MTH")
```

# Comparing to cox model formulas to optimise for best model

Function adapted from  http://rstudio-pubs-static.s3.amazonaws.com/16621_8843f393472f4e8793435462d8c4859e.html 

NOTE - 
""Oka suggested using frailty in connection with coxph in order to test the proportional hazard assumption. I believe it is worth noting that the documentation for frailty mentions, "the coxme package has superseded this [frailty] method." For this reason, the original question about "how to test the PH assumption on mixed effect cox model coxme," has strong justification to stay within the scope of coxme."" - Stack Overflow

USING COX.ZPH to check for the validity of Cox - https://stats.stackexchange.com/questions/254471/coxme-proportional-hazard-assumption 

```{r}
fit0 <- coxph(Surv(as.numeric(as.character(CTA_tumor$OS)), as.numeric(as.character(CTA_tumor$OS.01))) ~ 1, data=CTA_tumor)
fit1 <- coxph(Surv(as.numeric(as.character(CTA_tumor$OS)), as.numeric(as.character(CTA_tumor$OS.01))) ~ MS4A1, data=CTA_tumor)
#Random effects are specified in the formula by a parenthesised expression which contains a vertical bar separating effects on the left from grouping variables on the right. In the case above we read it as an intercept (effect) per center (group).
fit2 <- coxme(Surv(as.numeric(as.character(CTA_tumor$OS)), as.numeric(as.character(CTA_tumor$OS.01))) ~ MS4A1+ (1|PATID), data=CTA_tumor)

Compare_models(baseModel = fit0,coxphModel=fit1, coxmeModel=fit2)
```


# Cox regression models

## Tumor

### All tumor patients

```{r}
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_tumor)-n 
e <- ncol(CTA_tumor)

Inputlist_T <- Uni_multi_coxme(data = CTA_tumor, name = "Tumor All", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)

KMCatCurves(data = CTA_tumor, inputlist = rownames(Inputlist_T), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```


## Cytotoxic

### All Cytotoxic patients

```{r}
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_cyto)-n 
e <- ncol(CTA_cyto)

Inputlist_C <- Uni_multi_coxme(data = CTA_cyto, name = "Cytotoxic (All)", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)
```

```{r}
KMCatCurves(data = CTA_cyto, inputlist = rownames(Inputlist_C), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```

### Cytotoxic segmented "Tumor-rich area" 

```{r}
CTA_subset <- CTA_cyto %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_subset)-n 
e <- ncol(CTA_subset)


Inputlist_C_TR <- Uni_multi_coxme(data = CTA_subset, name = "Cytotoxic Tumor-rich area", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)

KMCatCurves(data = CTA_subset, inputlist = rownames(Inputlist_C_TR), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```

### Cytotoxic segmented "Tumor-sparse area" 

```{r}
CTA_subset <- CTA_cyto %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_subset)-n 
e <- ncol(CTA_subset)

Inputlist_C_TS <- Uni_multi_coxme(data = CTA_subset, name = "Cytotoxic Tumor-sparse area", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)

KMCatCurves(data = CTA_subset, inputlist = rownames(Inputlist_C_TS), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```


## Helper

### All Helper patients

```{r}
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_helper)-n 
e <- ncol(CTA_helper)

Inputlist_H <- Uni_multi_coxme(data = CTA_helper, name = "Helper (All)", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)
```

```{r}
KMCatCurves(data = CTA_helper, inputlist = rownames(Inputlist_H), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```

### Helper segmented "Tumor-rich area" 

```{r}
CTA_subset <- CTA_helper %>% dplyr::filter(Within.the.tumor=="Tumor-rich")
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_subset)-n 
e <- ncol(CTA_subset)

Inputlist_H_TR <- Uni_multi_coxme(data = CTA_subset, name = "Helper (Tumor-rich)", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)
```

```{r}
KMCatCurves(data = CTA_subset, inputlist = rownames(Inputlist_H_TR), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```

### Helper segmented "Tumor-sparse area" 

```{r}
CTA_subset <- CTA_helper %>% dplyr::filter(Within.the.tumor=="Tumor-sparse")
n <- 1481 ## total number of probes excluding NPC
s <- ncol(CTA_subset)-n 
e <- ncol(CTA_subset)

Inputlist_H_TS <- Uni_multi_coxme(data = CTA_subset, name = "Helper (Tumor-sparse)", s = s, e = e, uniquefactortype = NULL, significance = 0.05, outputfilepath = "CTA feature specific survival Result_images/", PATID = "PATID", SegmentLabel = "SegmentLabelNew", Time = "OS", Event = "OS.01", printforest = FALSE, multivariatetype = "Aggregated Mean", filterCV = FALSE, CVcutoff = 30)
```

```{r}
KMCatCurves(data = CTA_subset, inputlist = rownames(Inputlist_H_TS), filter = FALSE, filterCV = FALSE, PATID = "PATID", CVcutoff = 30, aggregationType = "mean", minprop = 0.1)
```
